### 2012-09-10 demo/taxize.Rmd
Added NCBI Taxonomy Browser example

# Install taxize (uncomment to run)
```{r}
# install_github("taxize_", "ropensci")
library(taxize); library(plyr); library(ape)
```

@@

## Get a TSN from a sepcies name
```{r}
get_tsn(searchterm = "Quercus_douglasii", searchtype = "sciname")
```

>>>>

# Install taxize (uncomment to run)
```{r}
# install_github("taxize_", "ropensci")
library(taxize); library(plyr); library(ape); library(XML); require(RCurl)
```

@@

## Get a TSN from a species name
```{r}
tsn <- get_tsn(searchterm = "Quercus_douglasii", searchtype = "sciname")
# use classification with get_tsn together:
classification(tsn)
```

# NCBI Taxonomy Browser
## Get Unique Identifier
```{r}
uids <- get_uid(c("Chironomus riparius", "Chaetopteryx"))
```

## And retrieve classification
```{r}
cl <- classification(uids)
cl
```
